{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-16 paper/tex/sections/results.tex
add formation channel description

\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}

@@

We show the formation channels through which the detectable DCOs formed in

Formation channel figure is Fig.~\ref{fig:formation_channels}.

\todo{@Selma will review this section}

@@

% \paragraph{Eccentricities}

% \todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}

>>>>

\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
\todo{@Selma will review this section}

@@

We show the fraction of detectable DCOs that formed through different formation channels in Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model that we describe in this section. Approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}. Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the `classic' channel and the rest are mainly formed through only stable mass transfer.

In contrast, detectable NSNSs are very rarely formed through only stable mass transfer. Approximately half of systems are formed through the `classic' channel and the rest are formed through a double-core common-envelope event \citep{Brown+1995} where both progenitors evolve on a similar timescale and initiate a double-core common-envelope event whilst they are on the giant branch. All detectable DCOs show a small fraction of systems are formed through a channel that does not fit into the other categories and hence are labelled `other'. These systems tend to be formed through `lucky' supernova kicks that happen to shrink the binary significantly by chance.

@@
